\documentclass[12pt]{article}
\usepackage{enumitem}

\title{API Technical Details Review}
\author{Enrique Ulises Báez Gómez Tagle}
\date{August 2023}

\begin{document}
\maketitle

\section{Architecture and Design}
\begin{itemize}
    \item \textbf{CRUD Operations}: Full support for Create, Read, Update, and Delete operations.
    \item \textbf{OAS (OpenAPI Specification)}: Technical documentation complying with OAS 3.0 or higher.
    \item \textbf{Idempotency}: Idempotent methods to ensure consistency.
\end{itemize}

\section{Security}
\begin{itemize}
    \item \textbf{OAuth 2.0/ JWT (JSON Web Tokens)}: Secure authentication and authorization.
    \item \textbf{TLS 1.2+}: Data encryption in transit.
    \item \textbf{Rate Limiting}: Limit the number of requests per user to prevent abuse.
    \item \textbf{WAF (Web Application Firewall)}: Additional protection against common web attacks.
\end{itemize}

\section{Scalability and Performance}
\begin{itemize}
    \item \textbf{Caching (Memcached/Redis)}: Use caching algorithms.
    \item \textbf{Load Balancing}: Traffic distribution across multiple servers.
    \item \textbf{Throttling}: Control access based on usage to prevent resource overload.
\end{itemize}

\section{Data}
\begin{itemize}
    \item \textbf{DBMS (Database Management System)}: Choice of database management system SQL.
    \item \textbf{ACID Transactions}: Ensure secure and reliable transactions.
    \item \textbf{ORM (Object-Relational Mapping)}: Mapping between objects and the database.
\end{itemize}

\section{Monitoring and Auditing}
\begin{itemize}
    \item \textbf{Logging}: Detailed recording of events and transactions.
    \item \textbf{APM (Application Performance Monitoring)}: Tools for monitoring health and performance.
    \item \textbf{Audit and Compliance}: Compliance review with GDPR, HIPAA, or other regulations.
\end{itemize}

\section{Interoperability}
\begin{itemize}
    \item \textbf{API Versioning}: Version control to ensure backward compatibility.
    \item \textbf{Internationalization}: Availability for student exchange program.
    \item \textbf{Webhooks}: For real-time events and notifications.
\end{itemize}

\section{Testing}
\begin{itemize}
    \item \textbf{Unit Testing}: Unit tests for each functional component.
    \item \textbf{Integration Testing}: Integration tests for complete workflows.
    \item \textbf{E2E (End-to-End) Testing}: Tests from start to finish in an environment similar to production.
\end{itemize}

\section{Documentation and SDK}
\begin{itemize}
    \item \textbf{Swagger or Postman Collections}: Tools for interactive documentation.
    \item \textbf{SDKs (Software Development Kits)}: Software development kits to facilitate integration.
\end{itemize}

\section{DevOps}
\begin{itemize}
    \item \textbf{CI/CD (Continuous Integration/Continuous Deployment)}: Automated pipelines for testing and deployment.
    \item \textbf{Docker/Kubernetes}: Containerization and orchestration to facilitate deployment and scalability.
\end{itemize}

\end{document}

